Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-29 ms.tex
cleaning up color correction discussion

% integral limits ??? check planck paper to see what they did

% now i need to define what \nu_{i,c} is (it's the nominal central 
% frequency of band \nu_i) e.g. 857 GHz for Planck 857, etc..

% also need to define what \mathcal{T} is (relative transmission, 
% dimensionless)

Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 3000\} GHz. 
$\mathcal{T}_{\nu_i}(\nu)$ represents the relative transmission as a function 
of frequency for band $\nu_i$. For the HFI maps, $\mathcal{T}_{\nu_i}(\nu)$ is 
given by the \PLANCK~transmission curves provided in the file 
\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. These bandpass correction 
factors are applied in the sense that $b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$
is a prediction suitable for comparison to the \PLANCK~data products.

>>>>

% integral limits ??? check planck paper to see what they did
% -> planck spectral response paper just leaves the integrals indefinite

Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 2997.92\} GHz. 
$\mathcal{T}_{\nu_i}(\nu)$ represents the relative transmission as a function 
of frequency for band $\nu_i$. For the HFI maps, $\mathcal{T}_{\nu_i}(\nu)$ is 
given by the \PLANCK~transmission curves provided in the file 
\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. The color correction factors
of Equation \ref{equ:bpcorr} are applied in the sense that 
$b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$ is a prediction suitable for 
direct comparison to the \PLANCK~data products.
